Communicating human related spatial distributions: A comparison of spatial visualisations using visual inference.

### 2020-01-08 paper/paper.Rmd
Add replicates table for exp design. Add examples of lineups

\begin{table}[]
\caption{The Experimental Design}
\label{tab:my-table}
\begin{tabular}{|l|l|l|}
\hline
Trend & Map type & Replicates \\ \hline
NW-SE & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
Three cities & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
All cities & Choropleth & 2 \\ \hline
 & Hexagon tile & 2 \\ \hline
\end{tabular}
\end{table}

@@

@@

d %>% group_by(type, trend) %>%
  summarise(m = round(mean(detect),3),
    std.dev = paste0("(", round(sd(detect),2),")")) %>% 
  gather(stat, value, m, std.dev) %>% 
  pivot_wider(names_from = "trend", values_from = "value") %>% 
  arrange(type) %>% ungroup() %>% 
  mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
  knitr::kable(., format = "latex", align = "lccc")
```

@@

```{r}
# Di playing
s <- d %>% group_by(type, trend, detect) %>%
  summarise(m=median(time_taken), 
            q1=quantile(time_taken, 0.25), 
            q3=quantile(time_taken, 0.75))
library(ggbeeswarm)
ggplot() + 
  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
  scale_colour_brewer(palette = "Dark2") +
  facet_grid(trend~detect)
```

The proportion of correct and incorrect responses within each 5 second time window. For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect. It is more likely that participants picked the correct response if they took longer to respond. For the Choropelth

@@

```{r reason, fig.cap = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. The facets show whether or not the choice was correct."}
###########################################################
# Qualitative analysis of reason
d %>% 
  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
  mutate(Detected = gsub("Detected? ", "", detect_f)) %>% 
  group_by(trend, Detected, type) %>% 
  count(reason) %>% 
  mutate(prop = round(n/sum(n), 3), r_prop = paste0(reason, ":", prop)) %>% 
  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
  pivot_wider(names_from = c("Detected"), values_from = c("reasons")) %>% 
  arrange(trend, type) %>% 
  select(Trend = trend, `Map Type` = type,
    `Yes` = `Detected? Yes`, `No` = `Detected? No`) %>% 
  knitr::kable(., format = "latex") %>% kable_styling("striped") %>%
  add_header_above(c(" " = 2, "Detected:" = 2))
```

@@

@@

```{r modeling_glm1}
# Modelling 
glm1 <- glm(formula = detect ~ type * trend,
  family = binomial(link = "logit"), data = d)

@@

factors <- c("Design", "", "Trend", "", "Interactions", "")
terms <- c("Intercept", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")

tidy(glm1) %>% 
  mutate(p.value = round(p.value, 4)) %>%
  mutate(sig = case_when(
    p.value <= 0.001 ~ "***", 
    p.value <= 0.01 ~ "**", 
    p.value <= 0.05 ~ "*", 
    p.value <= 0.01 ~ ".",
    TRUE ~ " ")) %>% 
  mutate(term = terms,
    factors = factors) %>% 
  select(`_` = factors, 
    terms = term, 
    Estimate = estimate, 
    Error = std.error, 
    Stat = statistic,
    p.value, sig) %>% knitr::kable(format = "latex", 
      align = "lrrrrl")
```

```{r}
d_glm <- d %>% select(group:certainty, detect, detect_f) %>%
  bind_cols(as_tibble(se.bands)) %>% 
  mutate(pfit, 
    predicted = ifelse(pfit > 0.5, 1, 0),
    predicted = factor(predicted, levels = c(0,1), 
      labels = c("Predicted: No", "Predicted: Yes")))

@@

```{r}
glm2 <- glm(formula = detect ~ type * trend + replicate_f,
  family = binomial(link = "logit"), data = d)

@@

int_2 <- confint(emmean2, by = c("type", "trend", "replicate_f"), adjust = "bonferroni")
int_2 %>% 
  ggplot(aes(x= replicate_f, y = prob, group = type)) + 
  geom_point(aes(col = type)) + 
  geom_line(alpha = 0.5, lty = "dashed") + 
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = replicate_f), 
                width = 0.2) +
  facet_grid(trend ~ .) +
  ylab("Estimated Marginal Mean")
```

```{r}
# Mixed effects models
lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
lmer1_d <- augment(lmer1, d)

@@

glance(lmer1)
tidy(lmer1)

d_lmer <- d %>% select(group:certainty, detect, detect_f) %>%
  bind_cols(as_tibble(se.bands)) %>% 
  mutate(pfit_lmer, 
    predicted = ifelse(pfit_lmer > 0.5, 1, 0),
    predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))

table(d_lmer$predicted, d_lmer$detect_f)

@@

```{r}
# Mixed effects models
lmer2 <- lmer(detect ~ (type|trend), data = d)
lmer2_d <- augment(lmer2, d)

@@

glance(lmer2)
tidy(lmer2)

@@

table(d_lmer2$predicted, d_lmer2$detect_f)
```

@@

```{r}
# Modelling 
lm1 <- lm(formula = as.numeric(certainty) ~ type, data = d)
lm1_d <- augment(lm1, d)
```

```{r}
# Mixed effects models
lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
lmer1

@@

```{r demogs}
# Create one record for each contributor, to examine demographics
dem_contribs <- d %>%
  group_by(contributor) %>%
  slice(1) %>% ungroup()

###############################################################################
# Demographics of contributors
#dem_contribs %>% count(gender)
dem_contribs %>% ggplot() + geom_bar(aes(age))
dem_contribs %>% count(gender)
dem_contribs %>% count(education)
dem_contribs %>% count(gender, education) %>% 
  spread(gender, n) %>% 
  mutate(`Col. Total` = He + She) %>% 
  gather("Gender", "Amount", He:`Col. Total`) %>% 
  spread(education, Amount) %>% 
  mutate(`Row Total` = Bach + `High School`, Masters,
    Gender = factor(Gender, levels = c("He", "She", "Col. Total"), labels = c("He", "She", "Col. Total"))) %>% knitr::kable(format = "latex")
```

>>>>

```{r exp_design, results = "asis"}
d %>% 
  mutate(Trend = trend,
    Group = group,
    `Map Type` = type) %>% 
  group_by(Group, Trend, `Map Type`) %>% 
  summarise(Reps = paste0(sort(unique(replicate)), collapse = ", ")) %>% 
  pivot_wider(names_from = c("Map Type"), values_from = c("Reps")) %>% 
  ungroup() %>% 
  knitr::kable(., format = "latex", booktabs = TRUE, caption = "Experimental design.") %>% kable_styling("striped") %>% 
  collapse_rows(., columns = 1, custom_latex_hline = c(1:3))
```

@@

Replicate 2 of the All Cities distribution is shown in XXX.

```{r cities_lineup, fig.cap = "The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled."}
#knitr::include_graphics("figures/aus_cities_3_geo.png")
```

!["The lineup of choropleth map displays shows a distribution that affects all capital cities. The values for the inner city areas in the capital cities result in them being coloured red. However, the colour blue dominates the display as the large rural areas are filled."](figures/aus_cities_3_geo.png)

```{r nwse_lineup, fig.cap = "A North-West to South East trend was hidden in this lineup of hexagon tile map displays."}
#knitr::include_graphics("figures/aus_nwse_6_hex.png")
```

!["A North-West to South East trend was hidden in this lineup of hexagon tile map displays."](figures/aus_nwse_6_hex.png)

@@

d %>% group_by(type, trend) %>%
  summarise(m = round(mean(detect),3),
    std.dev = paste0("(", round(sd(detect),2),")")) %>% 
  gather(stat, value, m, std.dev) %>% 
  pivot_wider(names_from = "trend", values_from = "value") %>% 
  arrange(type) %>% ungroup() %>% 
  mutate(Type = types) %>% select(Type, `NW-SE`, `Three Cities`, `All Cities`) %>%
  knitr::kable(., format = "latex", align = "lccc", booktabs = TRUE)
```

@@

```{r beeswarm, fig.cap = "The beeswarm plots show the distribution of the time taken to submit a response for each combination of trend and type of display. The time taken shown by the height of the point for each evaluationq1. The height of the histogram bars show how many evaulations were submitted within each time window. The orange regions of the bars show the amount of correct detections, and the green regions are the amount of incorrect detections."}
# Di playing
s <- d %>% group_by(type, trend, detect) %>%
  summarise(m=median(time_taken), 
            q1=quantile(time_taken, 0.25), 
            q3=quantile(time_taken, 0.75))
library(ggbeeswarm)
ggplot() + 
  geom_quasirandom(data=d, aes(x=type, y=time_taken), alpha=0.9) + 
  #geom_hline(data=s, aes(yintercept=m, colour=type)) +
  geom_point(data=s, aes(x=type, y=m, colour=type), size=5, alpha=0.7) +
  #geom_errorbar(data=s, aes(x=type, ymin=q1, ymax=q3, colour=type), width=0.3, size=2) +
  scale_colour_brewer(palette = "Dark2") +
  facet_grid(trend~detect)
```

The proportion of correct and incorrect responsesis shown by the width used to distribute the points horizontally. Each point is randomly placed, but regions with more points require points to be placed further from center. For the NW-SE distribution, it is equally likely that quick responders will be correct or incorrect. It is more likely that participants picked the correct response if they took longer to respond. For the Choropelth

@@

```{r reason, fig.cap = "The amount of participants that selected each reason for their choice of plot when looking at each trend model shown in Choropleth and Hexagon Tile maps. The facets show whether or not the choice was correct.", results = "asis"}

# Qualitative analysis of reason
d %>% 
  mutate(reason = ifelse(reason =="0.0", "no reason", reason)) %>% 
  mutate(Detected = ifelse(detect_f == "Detected? Yes", "Yes", "No"),
    Trend = trend) %>% 
  group_by(Trend, Detected, type) %>% 
  count(reason) %>% 
  mutate(prop = round(n/sum(n), 3), r_prop = paste0(reason, ":", prop)) %>% 
  top_n(1, n) %>% summarise(reasons = paste(reason, collapse=", ")) %>% 
  pivot_wider(names_from = c("type"), values_from = c("reasons")) %>% 
  ungroup() %>% 
  knitr::kable(., format = "latex", booktabs = TRUE) %>% kable_styling("striped") %>% 
  collapse_rows(., columns = 1, custom_latex_hline = c(1:2, 3:4))
```

@@

One lineup had extremely similiar detection rates for the Choropleth and Hexagon displays.

@@

```{r modeling_glm1, results="asis"}
# Modelling 
glm1 <- glm(formula = detect ~ type * trend,
  family = binomial(link = "logit"), data = d)

@@

terms <- c("Intercept", "Hex", "Three cities", "All cities", "Hex : Three cities", "Hex : All cities")

tidy(glm1) %>%
  mutate_if(is.numeric, round, 2) %>% 
  rowwise() %>% 
  mutate(estimate = case_when(
    p.value <= 0.001 ~ paste0(estimate,"$^{***}$"),
    p.value <= 0.01 ~ paste0(estimate, "$^{** }$"), 
    p.value <= 0.05 ~ paste0(estimate, "$^{*  }$"), 
    p.value <= 0.01 ~ paste0(estimate, "$^{.  }$"),
    TRUE ~ paste0(estimate))) %>% 
  ungroup() %>% 
  mutate(term = terms) %>% 
  select(Term = term, 
    Estimate = estimate, 
    Error = std.error, 
    Stat = statistic,
    p.value) %>% knitr::kable(format = "latex", escape = FALSE, align= "rcrrr", booktabs = T)
```

```{r pred_glm1}
d_glm <- d %>% select(group:certainty, detect, detect_f) %>%
  bind_cols(as_tibble(se.bands)) %>% 
  mutate(pfit, 
    predicted = ifelse(pfit > 0.5, 1, 0),
    predicted = factor(predicted, levels = c(0,1), 
      labels = c("Predicted: No", "Predicted: Yes")))

@@

```{r glm2}
glm2 <- glm(formula = detect ~ type * trend + replicate_f,
  family = binomial(link = "logit"), data = d)

@@

int_2 <- confint(emmean2, by = c("type", "trend", "replicate_f"), adjust = "bonferroni")
int_2 %>% 
  ggplot(aes(x= replicate_f, y = prob, group = type)) + 
  geom_point() + 
  geom_line(alpha = 0.5, lty = "dashed") + 
  geom_errorbar(aes(ymin = asymp.LCL, ymax = asymp.UCL, col = type), width = 0.2) +
  scale_color_manual(values = type_colours) +
  facet_grid(trend ~ .) +
  labs(x = "Replicates", y = "Detection Rate")
```

```{r lmer1, results = "asis"}
# Mixed effects models
lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
lmer1_d <- augment(lmer1, d)

@@

stargazer::stargazer(lmer1)

d_lmer <- d %>% select(group:certainty, detect, detect_f) %>%
  bind_cols(as_tibble(se.bands)) %>% 
  mutate(pfit_lmer, 
    predicted = ifelse(pfit_lmer > 0.5, 1, 0),
    predicted = factor(predicted, levels = c(0,1), labels = c("No", "Yes")))
# Hexagon maps have better chance of correct detection
# Allowing for contributor effects to vary: 0.12 strong residual
```

@@

```{r lmer2, results = "asis"}
# Mixed effects models
lmer2 <- lmer(detect ~ (type|trend), data = d)
lmer2_d <- augment(lmer2, d)

@@

stargazer::stargazer(lmer2)

@@

```

@@

```{r lmer1_model, results = "asis"}
# Mixed effects models
lmer1 <- lmer(detect ~ type*trend + (1|contributor), data = d)
tidy(lmer1) %>% mutate_if(is.numeric, .f = round, 2) %>% stargazer::stargazer(.)

@@

```{r demogs, results = "asis"}
# Create one record for each contributor, to examine demographics
dem_contribs <- d %>%
  group_by(contributor) %>%
  slice(1) %>% ungroup()

# Demographics of contributors
#dem_contribs %>% count(gender)
dem_contribs %>% ggplot() + geom_bar(aes(age))
dem_contribs %>% count(gender) %>% knitr::kable(format = "latex", booktabs = TRUE)
dem_contribs %>% count(education) %>% knitr::kable(format = "latex", booktabs = TRUE)
```
